Section rings of $\bq$-divisors on minimal rational surfaces

### 2018-01-09 surfaces-write-up/surface-paper.tex
fix section ref typo, delete comments
more typos found

\subsection{Modular Forms}
\label{subsection:modular-forms}
The work in this paper was motivated by 
potential applications to
calculating a presentation of certain rings of
Hilbert 
modular forms and Siegel modular forms. 
Recall that Hilbert and Siegel 
modular forms are two generalizations of modular forms to higher dimensions,
as described in \cite{geer:siegel-modular} and \cite{bruinier:hilbert-modular}.
%Voight and Zureick-Brown show that 
%one can translate the analytic category of 1-dimensional complex orbifolds to
%the algebraic category of stacky curves \cite[Proposition 6.1.5]{vzb:stacky}. 
%If one could generalize this result to yield an equivalence of
%categories between an appropriate subcategory of $m$-dimensional orbifolds and
%a subcategory of $m$-dimensional algebraic spaces,
%this would allow us to translate 
%rings of Hilbert modular forms
%and Siegel modular forms whose coarse space is a projective space or a
%Hirzebruch surface to canonical rings on the corresponding algebraic surfaces.
If the bounds given in 
Theorem~\ref{thm:proj-generators-relations} and Theorem~\ref{thm:hirz-generators-relations}
could be extended to all rational surfaces, instead of just minimal ones,
they would give a bound on generators and relations for 
rings of Hilbert and Siegel modular forms parameterized by rational
Hilbert and Siegel modular surfaces.
See Theorem~\ref{sec:conc} for a potential approach for generalizing our results to arbitrary rational surfaces.
This would be interesting because such modular surfaces tend to be
immensely complicated. 
%``Already for $g = 2$, the boundary of this fundamental domain is complicated; Gottschling found that it possesses $28$ boundary pieces'' \cite[p.\ 7]{geer:siegel-modular}.

@@

Every rational surface can be obtained from a minimal rational surface by a 
sequence of blow-ups \cite{eisenbud-harris:minimal}. Therefore, to answer
Question \ref{qn:general-minimal-surface} affirmatively, it suffices
to bound the degree of generators and relations of the 
section ring of a divisor on a blow-up of a given surface
in terms of the section 
rings of some associated divisors that given surface.

>>>>

\subsection{Modular Forms}
\label{subsection:modular-forms}
The work in this paper was motivated by 
potential applications to
calculating a presentation of certain rings of
Hilbert 
modular forms and Siegel modular forms. 
Recall that Hilbert and Siegel 
modular forms are two generalizations of modular forms to higher dimensions,
as described in \cite{geer:siegel-modular} and \cite{bruinier:hilbert-modular}.
%Voight and Zureick-Brown show that 
%one can translate the analytic category of 1-dimensional complex orbifolds to
%the algebraic category of stacky curves \cite[Proposition 6.1.5]{vzb:stacky}. 
%If one could generalize this result to yield an equivalence of
%categories between an appropriate subcategory of $m$-dimensional orbifolds and
%a subcategory of $m$-dimensional algebraic spaces,
%this would allow us to translate 
%rings of Hilbert modular forms
%and Siegel modular forms whose coarse space is a projective space or a
%Hirzebruch surface to canonical rings on the corresponding algebraic surfaces.
If the bounds given in 
Theorem~\ref{thm:proj-generators-relations} and Theorem~\ref{thm:hirz-generators-relations}
could be extended to all rational surfaces, instead of just minimal ones,
they would give a bound on generators and relations for 
rings of Hilbert and Siegel modular forms parametrized by rational
Hilbert and Siegel modular surfaces.
See Section~\ref{sec:conc} for a potential approach for generalizing our results to arbitrary rational surfaces.
This would be interesting because such modular surfaces tend to be
immensely complicated. 
%``Already for $g = 2$, the boundary of this fundamental domain is complicated; Gottschling found that it possesses $28$ boundary pieces'' \cite[p.\ 7]{geer:siegel-modular}.

@@

Every rational surface can be obtained from a minimal rational surface by a 
sequence of blow-ups \cite{eisenbud-harris:minimal}. Therefore, to answer
Question \ref{qn:general-minimal-surface} affirmatively, it suffices
to bound the degree of generators and relations of the 
section ring of a divisor on a blow-up of a given surface
in terms of the section 
rings of some associated divisors on that given surface.
